LaMachine: A meta-distribution for NLP software

### 2018-07-26 docs/lamachine_extabstract_clarin2018.tex
[paper] processed reviewer 1 comments

Being an open-source NLP software distribution, LaMachine is constrained to POSIX-compliant platforms; this primarily
means Linux, but also BSD and, with some restrictions, macOS. This stands in contrast with mobile platforms
(Android/iOS/etc), native Windows/mac desktop software, or certain interface types in general such as classical desktop
GUI applications, all of which fall beyond the scope of LaMachine. Software that is incorporated must 1) bear some
relevance to NLP, 2) be under a recognised open-source license, 3) be deposited in a public version controlled
repository\footnote{e.g. Github, Gitlab, Bitbucket} and 4) have a release protocol (with semantic versioning) using the
proper technology-specific channels.

>>>>

Being an open-source NLP software distribution, LaMachine is constrained to Unix-like platforms; this primarily means
Linux, but also BSD and, with some restrictions, macOS. Cygwin\footnote{A unix environment on Windows} is not tested or
supported. This constaint stands in contrast with mobile platforms (Android/iOS/etc), native Windows/mac desktop software, or
certain interface types in general such as classical desktop GUI applications, all of which fall beyond the scope of
LaMachine. Software that is incorporated must 1) bear some relevance to NLP, 2) be under a recognised open-source
license, 3) be deposited in a public version controlled repository\footnote{e.g. Github, Gitlab, Bitbucket, provided the
repository is public} and 4) have
a release protocol (with semantic versioning) using the proper technology-specific channels.
